Installation

### 2024-07-15 nbs/guides/installation.qmd
nit(guides): fix marker name
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

::: {#nte-blank-cells .callout-note collapse=true title="Architecture and accelerator support"}
If you would like to test pyrovelocity without requiring a GPU you should be
able to install it on any platform. However, if you would like to apply it to
data sets larger than $O(10^3)$ cells, you will need a GPU.
In this case, we can only support amd64 Linux systems with a CUDA compatible GPU.
If you are having issues scaling pyrovelocity please do not hesitate to reach out to us.
:::

>>>>

::: {#nte-architecture .callout-note collapse=true title="Architecture and accelerator support"}
If you would like to test pyrovelocity without requiring a GPU you should be
able to install it on any platform. However, if you would like to apply it to
data sets larger than $O(10^3)$ cells, you will need a GPU.
In this case, we can only support amd64 Linux systems with a CUDA compatible GPU.
If you are having issues scaling pyrovelocity please do not hesitate to reach out to us.
:::
